Grow with the flow: faster growth is associated with more variable precipitation in a perennial herb

### 2015-04-30 ms/ms.tex
Finished rough draft

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
  \hlcom{# The path to the ms directory may need to be changed for different users}
  \hlcom{# Manuscript files}
  \hlstd{pathMS} \hlkwb{<-} \hlstr{"~/Google Drive/CardLocalAdaptation/ms"} \hlcom{# Chris' MacBook}
  \hlcom{# pathMS <- "~/Documents/CardAdapt/ms" # Chris' Linux laptop}

  \hlcom{# Data files for paper}
  \hlstd{pathDat} \hlkwb{<-} \hlkwd{paste}\hlstd{(pathMS,} \hlstr{"/Data"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{)}

  \hlcom{# Figures for paper}
  \hlstd{pathFig} \hlkwb{<-} \hlkwd{paste}\hlstd{(pathMS,} \hlstr{"/Figures"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{)}

  \hlcom{# Tables for paper}
  \hlstd{pathTab} \hlkwb{<-} \hlkwd{paste}\hlstd{(pathMS,} \hlstr{"/Tables"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{)}

  \hlcom{# Small function to make statistical significance asterisks}
  \hlstd{sigStar} \hlkwb{<-} \hlkwa{function}\hlstd{(}\hlkwc{pvalue}\hlstd{)}
  \hlstd{\{}
    \hlkwa{if} \hlstd{(pvalue} \hlopt{>=} \hlnum{0.05}\hlstd{)} \hlkwd{return}\hlstd{(}\hlstr{""}\hlstd{)}
    \hlkwa{if} \hlstd{(pvalue} \hlopt{<} \hlnum{0.05} \hlopt{&} \hlstd{pvalue} \hlopt{>=} \hlnum{0.01}\hlstd{)} \hlkwd{return}\hlstd{(}\hlstr{"*"}\hlstd{)}
    \hlkwa{if} \hlstd{(pvalue} \hlopt{<} \hlnum{0.01} \hlopt{&} \hlstd{pvalue} \hlopt{>=} \hlnum{0.001}\hlstd{)} \hlkwd{return}\hlstd{(}\hlstr{"**"}\hlstd{)}
    \hlkwa{if} \hlstd{(pvalue} \hlopt{<} \hlnum{0.001}\hlstd{)} \hlkwd{return}\hlstd{(}\hlstr{"***"}\hlstd{)}
  \hlstd{\}}

  \hlcom{# Color palette}
  \hlcom{# Primary color:}

   \hlstd{primShade0} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{0}\hlstd{,} \hlnum{0.286}\hlstd{)}
   \hlstd{primShade1} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{0.643}\hlstd{,} \hlnum{0.745}\hlstd{)}
   \hlstd{primShade2} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{0.439}\hlstd{,} \hlnum{0.6}\hlstd{)}
   \hlstd{primShade3} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.765}\hlstd{,} \hlnum{0}\hlstd{,} \hlnum{0.22}\hlstd{)}
   \hlstd{primShade4} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.588}\hlstd{,} \hlnum{0}\hlstd{,} \hlnum{0.169}\hlstd{)}

  \hlcom{# Secondary color (1):}

  \hlstd{sec1shade0} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.008}\hlstd{,} \hlnum{0.957}\hlstd{,} \hlnum{1}\hlstd{)}
  \hlstd{sec1shade1} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.643}\hlstd{,} \hlnum{0.984}\hlstd{,} \hlnum{1}\hlstd{)}
  \hlstd{sec1shade2} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.443}\hlstd{,} \hlnum{0.976}\hlstd{,} \hlnum{1}\hlstd{)}
  \hlstd{sec1shade3} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.49}\hlstd{,} \hlnum{0.514}\hlstd{)}
  \hlstd{sec1shade4} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0.376}\hlstd{,} \hlnum{0.396}\hlstd{)}

  \hlcom{# Secondary color (2):}

  \hlstd{sec2shade0} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.988}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{0}\hlstd{)}
  \hlstd{sec2shade1} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.996}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{0.643}\hlstd{)}
  \hlstd{sec2shade2} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.992}\hlstd{,} \hlnum{1}\hlstd{,} \hlnum{0.439}\hlstd{)}
  \hlstd{sec2shade3} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.835}\hlstd{,} \hlnum{0.847}\hlstd{,} \hlnum{0}\hlstd{)}
  \hlstd{sec2shade4} \hlkwb{<-} \hlkwd{rgb}\hlstd{(}\hlnum{0.643}\hlstd{,} \hlnum{0.651}\hlstd{,} \hlnum{0}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\title{(working title) Local Physiological Adaptation in \textit{Mimulus cardinalis}}
\author{Christopher D. Muir and Amy L. Angert}
%\date{}							% Activate to display a given date or no date

%
% Start document
%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle
\listoffigures
\listoftables

@@

We used 16 populations from throughout the range of \textit{M. cardinalis} (Table 1). Seeds were collected in the field \cdm{Amy, can you explain seed collection methods?}.

\begin{table}[ht]
   \centering
   \topcaption{16 Focal populations}
   \begin{tabular}{@{} lllllll @{}}
      \toprule
  Name& Region  & Demo?& Pop gen?& Latitude  & Longtiude  & Elevation (mas) \\
      \midrule
	HAU & South Margin		& yes	& yes	& 32.657	& 
    \ensuremath{-116.532}	& 799   \\
	CTC	& South Margin		& yes	& no	& 32.609 & 
    \ensuremath{-116.7}	& 267   \\
	CUR	& South Margin		& yes	& yes & 32.9 & 
    \ensuremath{-116.585}	& 1180   \\
	GRP & South Margin		& no	& no	& 33.314 &
    \ensuremath{-116.871}	& 1577   \\
	WWC &	Transverse		  & yes	& yes	& 33.994 & 
    \ensuremath{-116.665}	& 705   \\
	MIL	& Transverse	  	& yes	& no	& 34.077 & 
    \ensuremath{-116.873}	& 2050   \\
	WFM	& Transverse	  	& yes	& no	& 34.284 & 
    \ensuremath{-117.378}	& 1120   \\
	NMT	& South Sierras		& yes	& yes?& 36.201 & 
    \ensuremath{-118.651}	& 1314   \\
	PRD	& South Sierras		& yes	& yes	& 36.518 & 
    \ensuremath{-118.759}	& 926   \\
	RWD	& South Sierras		& yes	& yes	& 36.691 & 
    \ensuremath{-118.91}	& 1727   \\
	WNA	& Central Sierras	& yes	& yes	& 37.541 & 
    \ensuremath{-119.649}	& 1224   \\
	RBW	& Central Sierras	& yes	& no	& 37.819 & 
    \ensuremath{-120.007}	& 876   \\
	MYU	& North Sierras		& yes	& yes	& 39.397 & 
    \ensuremath{-121.082}	& 455   \\
	LIJ	& North Sierras		& yes	& yes	& 39.743 & 
    \ensuremath{-120.704}	& 1603   \\
	DPC	& North Coast	  	& yes	& yes	& 41.668 & 
    \ensuremath{-123.11}	& 707   \\
	RCC	& North Margin		& yes	& yes	& 43.374 & 
    \ensuremath{-122.957}	& 326   \\
	\bottomrule
   \end{tabular}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(scales)} \hlcom{# for color transparency}
\hlstd{exptlDes} \hlkwb{<-} \hlkwd{read.csv}\hlstd{(}\hlkwd{paste}\hlstd{(pathDat,} \hlstr{"/ExperimentalDesign.csv"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{))}

\hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/ExperimentalDesignBase.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{7}\hlstd{,} \hlnum{5}\hlstd{)}
\hlkwd{par}\hlstd{(}\hlkwc{mai} \hlstd{=} \hlkwd{rep}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{4}\hlstd{))}
\hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlkwd{max}\hlstd{(exptlDes}\hlopt{$}\hlstd{DayN)),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlopt{-}\hlnum{1}\hlstd{,} \hlnum{41}\hlstd{),}
                 \hlkwc{axes} \hlstd{= F,} \hlkwc{frame.plot} \hlstd{= T,} \hlkwc{cex.lab} \hlstd{=} \hlnum{1.5}\hlstd{,} \hlkwc{xlab} \hlstd{=} \hlstr{"Key treatments and measurements"}\hlstd{,}
     \hlkwc{ylab} \hlstd{=} \hlkwd{expression}\hlstd{(}\hlkwd{paste}\hlstd{(}\hlstr{"Temperature ("}\hlstd{,} \hlkwd{phantom}\hlstd{()}\hlopt{*}\hlstd{degree,} \hlstr{"C)"}\hlstd{)))}

\hlcom{# Temperature axis}
\hlkwd{axis}\hlstd{(}\hlnum{2}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{40}\hlstd{,} \hlnum{10}\hlstd{),} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{las} \hlstd{=} \hlnum{1}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlkwd{c}\hlstd{(}\hlkwd{expression}\hlstd{(}\hlnum{0}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{10}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{20}\hlopt{*}\hlstd{degree),}
                                                 \hlkwd{expression}\hlstd{(}\hlnum{30}\hlopt{*}\hlstd{degree),} \hlkwd{expression}\hlstd{(}\hlnum{40}\hlopt{*}\hlstd{degree)))}
\hlcom{# Axis of time on top}
\hlkwd{mtext}\hlstd{(}\hlstr{"Days after sowing"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{3.5}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
\hlkwd{mtext}\hlstd{(}\hlstr{"(Date for climate simulation)"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{2.25}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{1.5}\hlstd{)}
\hlkwd{axis}\hlstd{(}\hlnum{3}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{seq}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{90}\hlstd{,} \hlnum{30}\hlstd{),} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{)}
\hlkwd{axis}\hlstd{(}\hlnum{3}\hlstd{,} \hlkwc{at} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{17}\hlstd{,} \hlnum{47}\hlstd{,} \hlnum{78}\hlstd{),} \hlkwc{lwd} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{lwd.ticks} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{line} \hlstd{=} \hlopt{-}\hlnum{0.5}\hlstd{,}
     \hlkwc{labels} \hlstd{=} \hlkwd{c}\hlstd{(}\hlstr{"(June)"}\hlstd{,} \hlstr{"(July)"}\hlstd{,} \hlstr{"(August)"}\hlstd{))}

\hlcom{# Indicate sowing, beginning of temperature and drought treatments}
\hlkwd{abline}\hlstd{(}\hlkwc{v} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
\hlkwd{mtext}\hlstd{(}\hlstr{"Sow"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlnum{0}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{0}\hlstd{)}
\hlkwd{abline}\hlstd{(}\hlkwc{v} \hlstd{=} \hlnum{17}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
\hlkwd{mtext}\hlstd{(}\hlstr{"Temp\textbackslash{}nTreatment"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlnum{17}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{1}\hlstd{)}
\hlkwd{abline}\hlstd{(}\hlkwc{v} \hlstd{=} \hlnum{37}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{lty} \hlstd{=} \hlnum{2}\hlstd{)}
\hlkwd{mtext}\hlstd{(}\hlstr{"Drought\textbackslash{}nTreatment"}\hlstd{,} \hlkwc{side} \hlstd{=} \hlnum{1}\hlstd{,} \hlkwc{at} \hlstd{=} \hlnum{37}\hlstd{,} \hlkwc{line} \hlstd{=} \hlnum{1}\hlstd{)}

\hlcom{# Polygon of Hot treatment, min and max}
\hlkwd{with}\hlstd{(exptlDes[}\hlnum{18}\hlopt{:}\hlnum{94}\hlstd{, ],} \hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{17}\hlopt{:}\hlnum{93}\hlstd{,} \hlnum{93}\hlopt{:}\hlnum{17}\hlstd{),} \hlkwd{c}\hlstd{(Tmin_hot,} \hlkwd{rev}\hlstd{(Tmax_hot)),}
  \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(primShade0,} \hlnum{0.25}\hlstd{)))}

\hlcom{# Polygon of Cool treatment, min and max}
\hlkwd{with}\hlstd{(exptlDes[}\hlnum{18}\hlopt{:}\hlnum{94}\hlstd{, ],} \hlkwd{polygon}\hlstd{(}\hlkwd{c}\hlstd{(}\hlnum{17}\hlopt{:}\hlnum{93}\hlstd{,} \hlnum{93}\hlopt{:}\hlnum{17}\hlstd{),} \hlkwd{c}\hlstd{(Tmin_cool,} \hlkwd{rev}\hlstd{(Tmax_cool)),}
  \hlkwc{border} \hlstd{=} \hlnum{NA}\hlstd{,} \hlkwc{col} \hlstd{=} \hlkwd{alpha}\hlstd{(sec1shade0,} \hlnum{0.25}\hlstd{)))}

\hlcom{# Lines with average temperature}
\hlkwd{with}\hlstd{(exptlDes[}\hlnum{18}\hlopt{:}\hlnum{94}\hlstd{, ],} \hlkwd{points}\hlstd{(}\hlnum{17}\hlopt{:}\hlnum{93}\hlstd{, Tavg_hot,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{,}
        \hlkwc{col} \hlstd{= primShade3))}
\hlkwd{with}\hlstd{(exptlDes[}\hlnum{18}\hlopt{:}\hlnum{94}\hlstd{, ],} \hlkwd{points}\hlstd{(}\hlnum{17}\hlopt{:}\hlnum{93}\hlstd{, Tavg_cool,} \hlkwc{lwd} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"l"}\hlstd{,}
        \hlkwc{col} \hlstd{= sec1shade3))}

\hlcom{# Rug indicating measurment timing}
\hlkwd{rect}\hlstd{(}\hlnum{6}\hlstd{,} \hlopt{-}\hlnum{2}\hlstd{,} \hlnum{17}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{)}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlnum{11.5}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{,} \hlkwc{labels} \hlstd{=} \hlstr{"Germ"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,}
  \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}

\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{rect}\hlstd{(}\hlkwd{min}\hlstd{(}\hlkwd{which}\hlstd{(LERmeas)),} \hlopt{-}\hlnum{2}\hlstd{,} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(LERmeas)),} \hlnum{0}\hlstd{,}
        \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{))}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlkwd{min}\hlstd{((}\hlkwd{which}\hlstd{(LERmeas))} \hlopt{+} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(LERmeas)))} \hlopt{/} \hlnum{2}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlstr{"LER"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}

\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{rect}\hlstd{(}\hlkwd{min}\hlstd{(}\hlkwd{which}\hlstd{(SERmeas)),} \hlnum{0}\hlstd{,} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(SERmeas)),} \hlnum{2}\hlstd{,}
        \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{))}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlkwd{min}\hlstd{((}\hlkwd{which}\hlstd{(SERmeas))} \hlopt{+} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(SERmeas)))} \hlopt{/} \hlnum{2}\hlstd{,} \hlnum{1}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlstr{"SER"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}

\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{rect}\hlstd{(}\hlkwd{min}\hlstd{(}\hlkwd{which}\hlstd{(Harvest)),} \hlopt{-}\hlnum{2}\hlstd{,} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(Harvest)),} \hlnum{0}\hlstd{,}
        \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{))}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlkwd{min}\hlstd{((}\hlkwd{which}\hlstd{(Harvest))} \hlopt{+} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(Harvest)))} \hlopt{/} \hlnum{2}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlstr{"Harvest"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}

\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{text}\hlstd{(}\hlkwd{min}\hlstd{((}\hlkwd{which}\hlstd{(PhotoMeas))} \hlopt{+} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(PhotoMeas)))} \hlopt{/} \hlnum{2}\hlstd{,} \hlnum{5}\hlstd{,}
        \hlkwc{labels} \hlstd{=} \hlstr{"Photo"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{,} \hlkwc{font} \hlstd{=} \hlnum{3}\hlstd{,} \hlkwc{cex} \hlstd{=} \hlnum{0.9}\hlstd{))}
\hlkwd{with}\hlstd{(exptlDes,} \hlkwd{rect}\hlstd{(}\hlkwd{min}\hlstd{(}\hlkwd{which}\hlstd{(PhotoMeas)),} \hlnum{2}\hlstd{,} \hlkwd{max}\hlstd{(}\hlkwd{which}\hlstd{(PhotoMeas)),} \hlnum{4}\hlstd{,}
        \hlkwc{border} \hlstd{=} \hlstr{"white"}\hlstd{,} \hlkwc{col} \hlstd{=} \hlstr{"grey"}\hlstd{))}
\hlcom{#with(exptlDes, text(min((which(PhotoMeas)) + max(which(PhotoMeas))) / 2, 3, }
\hlcom{#	labels = "Photo", col = "white", font = 3, cex = 0.9))}

\hlkwd{dev.off}\hlstd{()}
\end{alltt}
\begin{verbatim}
## pdf 
##   2
\end{verbatim}
\begin{alltt}
\hlcom{# Legend}
\hlkwd{pdf}\hlstd{(}\hlkwd{paste}\hlstd{(pathFig,} \hlstr{"/ExperimentalDesignLegend.pdf"}\hlstd{,} \hlkwc{sep} \hlstd{=} \hlstr{""}\hlstd{),} \hlnum{1.5}\hlstd{,} \hlnum{2}\hlstd{)}
\hlkwd{par}\hlstd{(}\hlkwc{mai} \hlstd{=} \hlkwd{rep}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{4}\hlstd{))}
\hlkwd{plot}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{0}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"n"}\hlstd{,} \hlkwc{xlim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{1.5}\hlstd{),} \hlkwc{ylim} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{0}\hlstd{,} \hlnum{1}\hlstd{),} \hlkwc{axes} \hlstd{= F)}

>>>>

@@

\title{Grow with the flow: faster growth is associated with more variable precipitation in a perennial herb}
\author{Christopher D. Muir$^{1,*}$ and Amy L. Angert$^1$}
\date{}

%
% Start document
%
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle

$^1$ Biodiversity Research Centre, University of British Columbia, Vancouver, BC, Canada

$^*$corresponding author: Chris Muir, cdmuir@biodiversity.ubc.ca

Original Article

Key words: local adaptation, photosynthesis, growth rate, climatic variance, \textit{Mimulus}

Word counts: TBA

3 figures; 3 tables; ? supporting files

Data will be archived on Dryad upon acceptance.

\clearpage

\listoffigures
\listoftables

@@

We used 16 populations from throughout the range of \textit{M. cardinalis} (Table~\ref{table:Table_FocalPops}). Seeds were collected in the field \cdm{Amy, can you explain seed collection methods?}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of focal population
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{table}[ht]
   \centering
   \topcaption[Focal Populations]{Geographic region, latitude, longitude, and elevation (mas = meters above seal level) of 16 focal populations used in this study.}
   \begin{tabular}{@{} lllllll @{}}
      \toprule
  Name& Region  & Demo?& Pop gen?& Latitude  & Longtiude  & Elevation (mas) \\
      \midrule
	HAU & South Margin		& yes	& yes	& 32.657	& 
    \ensuremath{-116.532}	& 799   \\
	CTC	& South Margin		& yes	& no	& 32.609 & 
    \ensuremath{-116.7}	& 267   \\
	CUR	& South Margin		& yes	& yes & 32.9 & 
    \ensuremath{-116.585}	& 1180   \\
	GRP & South Margin		& no	& no	& 33.314 &
    \ensuremath{-116.871}	& 1577   \\
	WWC &	Transverse		  & yes	& yes	& 33.994 & 
    \ensuremath{-116.665}	& 705   \\
	MIL	& Transverse	  	& yes	& no	& 34.077 & 
    \ensuremath{-116.873}	& 2050   \\
	WFM	& Transverse	  	& yes	& no	& 34.284 & 
    \ensuremath{-117.378}	& 1120   \\
	NMT	& South Sierras		& yes	& yes?& 36.201 & 
    \ensuremath{-118.651}	& 1314   \\
	PRD	& South Sierras		& yes	& yes	& 36.518 & 
    \ensuremath{-118.759}	& 926   \\
	RWD	& South Sierras		& yes	& yes	& 36.691 & 
    \ensuremath{-118.91}	& 1727   \\
	WNA	& Central Sierras	& yes	& yes	& 37.541 & 
    \ensuremath{-119.649}	& 1224   \\
	RBW	& Central Sierras	& yes	& no	& 37.819 & 
    \ensuremath{-120.007}	& 876   \\
	MYU	& North Sierras		& yes	& yes	& 39.397 & 
    \ensuremath{-121.082}	& 455   \\
	LIJ	& North Sierras		& yes	& yes	& 39.743 & 
    \ensuremath{-120.704}	& 1603   \\
	DPC	& North Coast	  	& yes	& yes	& 41.668 & 
    \ensuremath{-123.11}	& 707   \\
	RCC	& North Margin		& yes	& yes	& 43.374 & 
    \ensuremath{-122.957}	& 326   \\
	\bottomrule
	\end{tabular}
	\label{table:Table_FocalPops}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figure summarizing experimental design
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h!]
	\centerline{\includegraphics[width=1\textwidth]{Figures/Figure_ExptlDes.pdf}}
	\usefont{T1}{phv}{m}{n}
	\fontsize{10}{12}
	\selectfont
	\caption[Experimental Design]{Overview of experimental treatments and timing of key trait measurements. All plants germinated within 21 days of sowing. At that time, we began temperature treatments (left axis), simulating a typical June-August weather pattern at Hot (red) and Cold (blue) sites. The bold lines track the average daily temperatures. Within each day, there was a maximum daytime temperture (top of translucent polygons) and minimum nighttime temperature (bottom of translucent polygons). The drought treatment commenced later by ramping down the frequency of bottom-watering episodes (black line; right axis). Grey boxes on the bottom of the plot outline the period of key measurements described in the Methods.}
	\label{fig:Fig_ExptlDes}
\end{figure}
